Suplementary Material 2: Drawing Publication Plots

### 2023-03-27 S1_replicate_stats_and_plots.Rmd
change figure labeles

## Data Import 8 European Populations

@@

```{r}
all_tbls$Dataset  <- rep(c("All births", "Without last birth"),2)
all_tbls$Populations  <- rep(c("8 European", "Estonia"),each=2)
all_tbls <- as.data.frame(all_tbls)
row.names(all_tbls) <- paste0(all_tbls$Populations, " populations ",
                              tolower(all_tbls$Dataset)) 
knitr::kable(t(all_tbls),
             caption = paste0("Summary data on the Estonian and other ",
                               "European populations for both ",
                              "all births and wihout last birth for same mothers"))
```

@@

```{r, fig.height=11.7/2, fig.width=8.3}
infoTxt <- "model prediction with 95% CI and data mean SE"
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    stat_summary(data=dmm_EE[dmm_EE$births_total <17, ],
                 aes(x=births_total, y=prob_twin, color="Estonia", fill = "Estonia"),
                 alpha=0.5,
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_EE_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data,
             aes(y = estimate,  x=births_total, color="8 European"),  size = 1) +
    stat_summary(data=dmm_orig[dmm_orig$births_total <19, ],
                 aes(x=births_total, y=prob_twin,
                     color="8 European", fill="8 European"),
                 alpha=0.5,
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_orig_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="8 European"),
                alpha = 0.3) +
    ggplot2::scale_x_continuous(breaks = 1:18) + 
    ggplot2::scale_y_continuous(breaks = seq(0,0.03, by=0.005)) +
    ggplot2::coord_cartesian() +
    labs(subtitle = paste0("All births, ", infoTxt),
         y="Per-birth twin. prob.",
         x="Maternal total births")
p2 <- fig2_ext_orig + base_theme(larger=8) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "population")

@@

```{r, fig.height=11.7/2, fig.width=8.3}
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data_nl,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    stat_summary(data=dmm_EE_nl_plot,
                 aes(x=births_total, y=prob_twin, color="Estonia", fill = "Estonia"),
                 alpha=0.5,
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_EE_plot_data_nl,
                aes(y = estimate, x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data_nl,
             aes(y = estimate,  x=births_total, color="8 European"),  size = 1) +
    stat_summary(data=dmm_orig_nl_plot,
                 aes(x=births_total, y=prob_twin,
                     color="8 European", fill="8 European"),
                 alpha=0.5,
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_orig_plot_data_nl,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="8 European"),
                alpha = 0.3) +
    ggplot2::scale_x_continuous(breaks = 1:18, limits = c(1,NA)) + 
    ggplot2::scale_y_continuous(breaks = seq(0,0.03, by=0.005)) +
    ggplot2::coord_cartesian(ylim=c(0,0.03)) +
    labs(subtitle = paste0("Without last birth, ", infoTxt),
         y="Per-birth twin. prob.",
         x="Maternal total births")
p3 <- fig2_ext_orig + base_theme(larger=8) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "population")

@@

fig2a <- draw_fig_4C(fig4C_orig_plot_data) + 
  labs(subtitle = "(A) 8 European pop., all births")

@@

fig2c <- draw_fig_4C(fig4C_orig_nl_plot_data, y_lims = c(0.01, 0.035)) + 
  labs(subtitle = "(C) 8 European pop., without last birth")

>>>>

## Data Import 9 Western European Populations

@@

```{r}
all_tbls$Dataset  <- rep(c("All births", "Without last birth"),2)
all_tbls$Populations  <- rep(c("9 Western European", "Estonia"),each=2)
all_tbls <- as.data.frame(all_tbls)
row.names(all_tbls) <- paste0(all_tbls$Populations, " populations ",
                              tolower(all_tbls$Dataset)) 
knitr::kable(t(all_tbls),
             caption = paste0("Summary data on the Estonian and other ",
                               "European populations for both ",
                              "all births and wihout last birth for same mothers"))
```

@@

```{r, fig.height=11.7/2, fig.width=8.3}
infoTxt <- "model prediction with 95% CI and data mean SE"
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    stat_summary(data=dmm_EE[dmm_EE$births_total <17, ],
                 aes(x=births_total, y=prob_twin, color="Estonia", fill = "Estonia"),
                 alpha=0.5,
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_EE_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data,
             aes(y = estimate,  x=births_total, color="9 W-European"),  size = 1) +
    stat_summary(data=dmm_orig[dmm_orig$births_total <19, ],
                 aes(x=births_total, y=prob_twin,
                     color="9 W-European", fill="9 W-European"),
                 alpha=0.5,
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_orig_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="9 W-European"),
                alpha = 0.3) +
    ggplot2::scale_x_continuous(breaks = 1:18) + 
    ggplot2::scale_y_continuous(breaks = seq(0,0.03, by=0.005)) +
    ggplot2::coord_cartesian() +
    labs(subtitle = paste0("All births, ", infoTxt),
         y="Per-birth twin. prob.",
         x="Maternal total births")
p2 <- fig2_ext_orig + base_theme(larger=8) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "population")

@@

```{r, fig.height=11.7/2, fig.width=8.3}
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data_nl,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    stat_summary(data=dmm_EE_nl_plot,
                 aes(x=births_total, y=prob_twin, color="Estonia", fill = "Estonia"),
                 alpha=0.5,
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_EE_plot_data_nl,
                aes(y = estimate, x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data_nl,
             aes(y = estimate,  x=births_total, color="9 W-European"),  size = 1) +
    stat_summary(data=dmm_orig_nl_plot,
                 aes(x=births_total, y=prob_twin,
                     color="9 W-European", fill="9 W-European"),
                 alpha=0.5,
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_orig_plot_data_nl,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="9 W-European"),
                alpha = 0.3) +
    ggplot2::scale_x_continuous(breaks = 1:18, limits = c(1,NA)) + 
    ggplot2::scale_y_continuous(breaks = seq(0,0.03, by=0.005)) +
    ggplot2::coord_cartesian(ylim=c(0,0.03)) +
    labs(subtitle = paste0("Without last birth, ", infoTxt),
         y="Per-birth twin. prob.",
         x="Maternal total births")
p3 <- fig2_ext_orig + base_theme(larger=8) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "population")

@@

fig2a <- draw_fig_4C(fig4C_orig_plot_data) + 
  labs(subtitle = "(A) 9 W-European pop., all births")

@@

fig2c <- draw_fig_4C(fig4C_orig_nl_plot_data, y_lims = c(0.01, 0.035)) + 
  labs(subtitle = "(C) 9 W-European pop., without last birth")

### 2023-03-27 S2_draw_publication_plots.Rmd
change figure labeles

```{r}
predDir <- ("./data/predictions/")
dmm_EE_fit <- readRDS(paste0(predDir,"dmm_EEdata_fig.rds"))
dmm_orig_fit <- readRDS(paste0(predDir,"dmm_origdata_fig.rds" ))
dmm_EE_nl_fit <- readRDS(paste0(predDir,"dmm_EE_nldata_fig.rds"))
dmm_orig_nl_fit <- readRDS(paste0(predDir,"dmm_orig_nldata_fig.rds"))
```

@@

```{r}
dmm_EE_nl_plot <- dmm_EE_nl
dmm_orig_nl_plot <- dmm_orig_nl
dmm_EE_nl_plot$births_total <- dmm_EE_nl_plot$births_total + 1
dmm_orig_nl_plot$births_total <- dmm_orig_nl_plot$births_total + 1
```

@@

fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    geom_ribbon(data=fig2_EE_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data,
             aes(y = estimate,  x=births_total, color="8 European populations"),  size = 1) +
    geom_ribbon(data=fig2_orig_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="8 European populations"),
                alpha = 0.3) +
    ggplot2::scale_x_continuous(breaks = 1:18) + 
    ggplot2::scale_y_continuous(trans = "logit",
                                breaks = seq(0.005, 0.025, by = 0.001)) +
    ggplot2::coord_cartesian() +
    labs(subtitle = "(A) Complete datasets",
         y="Per-birth twinning probability",
         x="Maternal total births")
p2 <- fig2_ext_orig + base_theme(larger=5, legend_pos = c(0.5,0.9)) + scale_color_manual(values=bc) + 
   scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "")

@@

```{r}
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data_nl,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    geom_ribbon(data=fig2_EE_plot_data_nl,
                aes(y = estimate, x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data_nl,
             aes(y = estimate,  x=births_total, color="8 European populations"),  size = 1) +
    geom_ribbon(data=fig2_orig_plot_data_nl,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="8 European populations"),
                alpha = 0.3) +
    ggplot2::scale_x_continuous(breaks = 1:18, limits = c(1,NA)) + 
    ggplot2::scale_y_continuous(trans = "logit",
                                breaks = seq(0.005, 0.025, by = 0.001)) +
    labs(subtitle = "(B) Without last births",
         y="Per-birth twinning probability",
         x="Maternal total births")
p3 <- fig2_ext_orig + base_theme(larger=5, legend_pos = "none") + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "")

>>>>

```{r}
predDir <- ("./data/predictions/")
eeForm <- "cbind(twin_total,singleton_total)~1+births_total" 
origForm <- "cbind(twin_total,singleton_total)~1+births_total+(1_x_pop)"
dmm_EE_fit <- readRDS(paste0(predDir, eeForm, "dmm_EEdata_fig.rds"))
dmm_orig_fit <- readRDS(paste0(predDir, origForm, "dmm_origdata_fig.rds" ))
dmm_EE_nl_fit <- readRDS(paste0(predDir, eeForm, "dmm_EE_nldata_fig.rds"))
dmm_orig_nl_fit <- readRDS(paste0(predDir, origForm, "dmm_orig_nldata_fig.rds"))
```

@@

@@

fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data,
            aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
  geom_ribbon(data=fig2_EE_plot_data,
              aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                  color="Estonia", fill = "Estonia"),
              alpha = 0.3) + 
  geom_line(data=fig2_orig_plot_data,
            aes(y = estimate,  x=births_total, color="9 W-European populations"),  size = 1) +
  geom_ribbon(data=fig2_orig_plot_data,
              aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                  fill="9 W-European populations"),
              alpha = 0.3) +
  ggplot2::scale_x_continuous(breaks = 1:18) + 
  ggplot2::scale_y_continuous(trans = "logit",
                              breaks = seq(0.005, 0.025, by = 0.001)) +
  ggplot2::coord_cartesian() +
  labs(subtitle = "(A) Complete datasets",
       y="Per-birth twinning probability",
       x="Maternal total births")
p2 <- fig2_ext_orig + base_theme(larger=5, legend_pos = c(0.5,0.9)) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "")

@@

```{r}
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data_nl,
            aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
  geom_ribbon(data=fig2_EE_plot_data_nl,
              aes(y = estimate, x=births_total, ymin = lwr, ymax = upr,
                  color="Estonia", fill = "Estonia"),
              alpha = 0.3) + 
  geom_line(data=fig2_orig_plot_data_nl,
            aes(y = estimate,  x=births_total, color="9 W-European populations"),  size = 1) +
  geom_ribbon(data=fig2_orig_plot_data_nl,
              aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                  fill="9 W-European populations"),
              alpha = 0.3) +
  ggplot2::scale_x_continuous(breaks = 1:18, limits = c(1,NA)) + 
  ggplot2::scale_y_continuous(trans = "logit",
                              breaks = seq(0.005, 0.025, by = 0.001)) +
  labs(subtitle = "(B) Without last births",
       y="Per-birth twinning probability",
       x="Maternal total births")
p3 <- fig2_ext_orig + base_theme(larger=5, legend_pos = "none") + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "")
